---
title: "Test Summary"
output: github_document
params:
  input_dir: './build'
---

```{r setup, include=FALSE}
# Config knitr
knitr::opts_chunk$set(echo = TRUE)
# Load all build artifacts 
data_files <- list.files(params$input_dir, pattern = "\\.dat$", full.names = TRUE)
lapply(data_files, load, .GlobalEnv)

```

## Summary Statistics from Raw Data

```{r raw_data_stats}

```

## Summary Statistics of Processed Data 

```{r proc_data_stats}

```

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
